---
title: "Analysis - task_6"
output:
  html_document:
    keep_md: yes
    df_print: kable
date: '2022-03-31'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries and reading data

```{r}
library(tidyverse)
library(here)

dogs <- read_csv(here("task_4/clean_data/dogs_clean.csv"))
```

# The client only counts a valid email address as one ending in ‘.com’. How many survey results have a valid email address.

```{r}
dogs %>% 
  filter(str_detect(email, ".com$")) %>% 
  nrow()
```


# What’s the average amount spent on dog food for each dog size.

```{r}
dogs %>% 
  filter(!is.na(dog_size)) %>% 
  group_by(dog_size) %>% 
  summarise(avg_amount = mean(amount_spent_on_dog_food, na.rm = TRUE))
```


# For owners whose surname starts with a letter in the second half of the alphabet (N onwards) what is the average age of their dog?

```{r}
dogs %>% 
  filter(str_detect(last_name, "^[N-Z]")) %>% 
  summarise(avg_age = mean(dog_age, na.rm = TRUE))
```


# The dog_age column is the age in dog years. If the conversion is 1 human year = 6 dog years, then what is the average human age for dogs of each gender?

```{r}
dogs %>% 
  filter(!is.na(dog_gender)) %>% 
  group_by(dog_gender) %>% 
  summarise(avg_human_age = mean(dog_age, na.rm = TRUE)/6)
```


# Create a plot of results of question 4.
