---
title: "task_2 - Analysis"
output: html_document
date: '2022-03-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading in Data and Libraries

```{r, results FALSE}
library(tidyverse)
library(here)

cakes <- read_csv(here("task_2/clean_data/cake_clean.csv"))
```

# 1. Which cake has the most cocoa in it?

```{r}
cakes %>%
  filter(ingredient == "cocoa") %>% 
  slice_max(amount)
```

# 2. For sponge cake, how many cups of ingredients are used in total?

```{r}
cakes %>% 
  filter(cake == "sponge") %>% 
  summarise()
```

# 3. How many ingredients are measured in teaspoons?

```{r}
cakes %>% 
  distinct(ingredient, measure) %>% 
  filter(measure == "teaspoon") %>% 
  nrow()
```

# 4. Which cake has the most unique ingredients?

I have defined the most unique cake to be the one with the most unique ingredients
(a unique ingredient being one only used in one cake)

```{r}
cakes %>% 
  mutate(amount = na_if(amount, 0)) %>% 
  drop_na(amount) %>% 
  group_by(ingredient) %>% 
  mutate(ingredient_no = n()) %>% 
  ungroup() %>% 
  filter(ingredient_no == 1) %>% 
  group_by(cake) %>% 
  summarise(no_unique_ingredients = n()) %>% 
  slice_max(no_unique_ingredients)
```

# 5. Which ingredients are used only once?

```{r}
cakes %>% 
  mutate(amount = na_if(amount, 0)) %>% 
  drop_na(amount) %>% 
  group_by(ingredient) %>% 
  summarise(no_occurences = n()) %>% 
  filter(no_occurences == 1)
```

