---
title: "Analysis - task_5"
output:
  html_document:
    keep_md: yes
    df_print: kable
date: '2022-03-31'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in data and loading libraries

```{r}
library(tidyverse)
library(here)

rwa <- read_csv(here("task_5/clean_data/rwa_clean.csv"))
```

# 1. What’s the average RWA score for each gender?

```{r}
rwa %>% 
  group_by(gender) %>% 
  summarise(avg_rwa_score = mean(rwa_score))
```

# 2. What’s the average RWA score for left handed people vs. right handed people.

```{r}
rwa %>% 
  group_by(hand) %>% 
  summarise(avg_rwa_score = mean(rwa_score), number_of_people = n())
```

# 3. What’s the average family size for each type of childhood?

```{r}
rwa %>% 
  group_by(urban) %>% 
  summarise(avg_family_size = mean(familysize))
```


# 4. What’s the average time to take the test for each education level?

```{r}
rwa %>% 
  group_by(education) %>% 
  summarise(avg_test_time = mean(testelapse))
```


# 5. Create a plot of results of question 4.

```{r}

```


# 6. What’s the average RWA score for people based on age

```{r}
rwa %>% 
  group_by(age_cat) %>% 
  summarise(avg_rwa_score = mean(rwa_score), number_of_people = n()) %>% 
  arrange(avg_rwa_score)
```

