---
title: "Analysis"
output: html_document
date: '2022-03-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in the libraries and clean data

```{r}
library(tidyverse)
library(here)

decathlon <- read_csv(here("task_1/clean_data/decathlon_clean.csv"))
```

# 1. Who had the longest long jump seen in the data?

```{r}
decathlon %>% 
  slice_max(long_jump)
```

# 2. What was the average 100m time in each competition?

```{r}
decathlon %>% 
  group_by(competition) %>% 
  summarise(avg_100m_time = mean(x100m))
```

# 3. Who had the highest total points across both competitions?

```{r}
decathlon %>% 
  group_by(name) %>% 
  summarise(total_points = sum(points)) %>% 
  slice_max(total_points)
```

# 4. What was the shot-put scores for the top three competitors in each competition?

```{r}
decathlon %>%
  group_by(competition) %>% 
  slice_max(shot_put, n = 3) %>% 
  select(competition, name, shot_put)
```

# 5. What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

## We have some competitors who have run both under 50s and over 50s but we can just include them in both under 50s and over

## Less than 50s

```{r}
decathlon %>% 
  filter(x400m < 50) %>% 
  group_by(name) %>% 
  summarise(competitor_points = mean(points)) %>% 
  summarise(overall_point_avg = mean(competitor_points))
```

## More than 50s

```{r}
decathlon %>% 
  filter(x400m > 50) %>% 
  group_by(name) %>% 
  summarise(competitor_points = mean(points)) %>% 
  summarise(overall_point_avg = mean(competitor_points))
```
